\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-06-03 paper/paper.tex
Added discussion piece and made small edits to first part.

While the GLFP model allows for multiple hazard functions, it does not account for the group structure of the hard drive data.  A naive approach would combine all drive models and fit an overall GLFP model.  This model can be easily estimated, but a common GLFP model for all drive brand groups fits poorly: the model captures drive models with lots of observed failures, while the predicted time to failure for drive brand models with less information is over or under estimated.  At the other extreme, fitting individual models to each hard drive brand excludes many drive brand models with fewer than 5 failures.  The GLFP model applied to these data produces very imprecise parameter estimates or can only be fit if highly informative priors are imposed.  \\

We therefore propose to fit the GLFP model using a hierarchical Bayesian approach.  With over 60 brand drive models in testing a hierarchical model is advantageous as it pools information from across brands to get more precise estimates of the GLFP parameters for each drive model group.  Moreover, the hierarchical model is a nice compromise between the aggregate and individual modeling approaches: drive models with lots of failures are estimated precisely; and in cases where little data is available the hierarchical model borrows information from other drive brand models to obtain stable estimates.  This allows us to include all of the hard drive data and more importantly, make valid inferences for each group of hard drive brands.

\subsection{Overview}
The structure of the paper is as follows.  Section 1 summarizes the Backblaze data and the unique modeling challenges it presents.  Section 2 introduces the GLFP model as a mixture of two Weibull distributions.  In Section 3 we fit multiple specifications of the GLFP model to best describe the Backblaze data.  We also discuss computational and modeling issues that suggest a final model with a common Weibull distribution for defective units and individual Weibull distributions for the wearout failure mode.  In Section 4 we compare hard drive brand models based on our final GLFP model.  Finally, in Section 5, we review the GLFP model and propose future extensions.

@@

As of the first quarter of 2016, Backblaze was collecting data on 63 different hard drive models.  Some drive models have been running since 2013, while others were added at a later date.  There are a total of 75,297 hard drives in operation.  The distribution of drives by model varies: some models have only have a service record for a single drive whereas the maximum number of service records for a single drive model is 35,860.  Figure \ref{fig1} shows the distribution of total number of failures and total observed time on test for drive brand models with at least 3 failures.  For model identification, a minimum of 3 failures was the criterion for hard drive brands to be included in the GLFP model.

@@

\subsection{Computation}
Each model was fit using the {\tt
  rstan}\cite{rstan} package in {\tt R} \cite{r}, which implements a variant of Hamiltonian Monte Carlo (HMC)
\cite{betancourt}. Multiple chain were run for 1500 iterations after 1500 warmup iterations. Convergence was assessed by examining posterior
plots and checking that potential scale reduction factors (Rhat) \cite{gelman2014bayesian} were less than $1.1$. Four chains were run for models 1,2 and 3 and 16 chains were run for model 4.

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{fig/heterogeneity-compare-preliminary}
\caption{Left: Kaplan-Meier estimates of the time to failure for each of the drive-models in the Backblaze data. Right: Pointwise posterior median time to failure curves for Models 1-4, orderered left to right, top to bottom.}
\label{fig2}
\end{figure}

\begin{figure}[H]
    \centering
   \includegraphics[width=\textwidth]{fig/mod_compare_legend}
		\caption{Estimated GLFP for 4 Drive Brand Models plotted on Weibull paper.  Black step function is the truncated adjusted Kaplan Meier points.  \label{fig:first}} 
\end{figure}

In addition to graphically examining model fits via posterior credible bands, we compared the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with the $i$th data point removed.  The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).  We computed the elpd for all 4 models using the R package loo \cite{loo}.  When $n$ is large, the distribution of the elpd is approximately normal and different models can be statistically compared.  We calculated the difference in expected predictive accuracy for Model 4 vs 3, Model 3 vs 2, and Model 2 vs 1, as well as the standard error of the difference (Table 1).  As the model complexity increased, the expected predictive accuracy improved.  Of all the models, Model 4 had the best predictive accuracy and was significantly better than the other 3 model specifications.

>>>>

While the GLFP model allows for multiple hazard functions, it does not account for the group structure of the hard drive data.  A naive approach would combine all drive models and fit an overall GLFP model.  This model can be easily estimated, but a common GLFP model for all drive brand groups fits poorly: the model captures drive models with lots of observed failures, while the predicted time to failure for drive brand models with less information is over or under estimated.  At the other extreme, fitting individual models to each hard drive brand excludes many drive brand models with few failures.  The GLFP model applied to these data produces very imprecise parameter estimates or can only be fit if highly informative priors are imposed.  \\

We therefore propose to fit the GLFP model using a hierarchical Bayesian approach.  With over 60 brand drive models in testing a hierarchical model is advantageous as it pools information from across brands to get more precise estimates of the GLFP parameters for each drive model group.  Moreover, the hierarchical model is a nice compromise between the aggregate and individual modeling approaches: drive models with lots of failures are estimated precisely; and in cases where little data is available the hierarchical model borrows information from other drive brand models to obtain stable estimates.  This allows us to include more of the hard drive data and more importantly, make valid inferences for each group of hard drive brands.

\subsection{Overview}
The structure of the paper is as follows.  Section 1 summarizes the Backblaze data and the unique modeling challenges it presents.  Section 2 introduces the GLFP model as a mixture of two Weibull distributions.  In Section 3 we fit multiple specifications of the GLFP model to best describe the Backblaze data.  We also discuss computational and modeling issues that suggest a final model with a common Weibull distribution for defective units and individual Weibull distributions for the wearout failure mode.  In Section 4 we compare the different model specifications, in addition to the hard drive brand models based on our final GLFP model.  Finally, in Section 5, we review the GLFP model and propose future extensions.

@@

As of the first quarter of 2016, Backblaze was collecting data on 63 different hard drive models.  Some drive models have been running since 2013, while others were added at a later date.  There are a total of 75,297 hard drives in operation.  The distribution of drives by model varies: some models have only have a service record for a single drive whereas the maximum number of service records for a single drive model is 35,860.  Figure \ref{fig1} shows the distribution of total number of failures and total observed running time for drive brand models with at least 3 failures.  For model identification, a minimum of 3 failures was the criterion for hard drive brands to be included in the GLFP model.

@@

\subsection{Computation}
Each model was fit using the {\tt
  rstan}\cite{rstan} package in {\tt R} \cite{r}, which implements a variant of Hamiltonian Monte Carlo (HMC)
\cite{betancourt}. Multiple chain were run for 1500 iterations after 1500 warmup iterations. Convergence was assessed by examining posterior
plots and checking that potential scale reduction factors (Rhat) \cite{gelman2014bayesian} were less than $1.1$. Four chains were run for Models 1,2 and 3 and 16 chains were run for Model 4.

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{fig/heterogeneity-compare-preliminary}
\caption{Left: Kaplan-Meier estimates of the time to failure for each of the drive-models in the Backblaze data. Right: Pointwise posterior median time to failure curves for Models 1-4, ordered left to right, top to bottom.}
\label{fig2}
\end{figure}

We can also compare the model fits for each drive brand model individually.  Using the set of parameters that maximize the posterior log probability, we examine the GLFP cdf for each of the 4 model specifications.  The GLFP fit for drive brand models 2, 9, 14, and 40 are presented in Figure 4.  The black step function again corresponds to the adjusted Kaplan-Meier estimates.  As model complexity increases, the GLFP curves become more flexible and are better able to fit the observed failure data.  All the GLFP models overestimate the proportion of failed hard drives for drive model 2, but Model 4 is the least biased.  For drive model 14, Models 1-3 underestimate the proportion of drives failing, and for drive model 40, they slightly overestimate the data.  Conversely, Model 4 follows the observed failures quite closely--accurately capturing failures at the lower and upper ends of the distribution.  The difference in accuracy between Models 3 and 4 are and Models 1 and 2 are visually quite apparent.  Differentiating between Model 3 and 4 is less clear; for instance, the fits from Model 3 and 4 line almost exactly on top of each other for drive model 40.
\begin{figure}[H]
    \centering
   \includegraphics[width=\textwidth]{fig/mod_compare_legend}
		\caption{Estimated GLFP for 4 Drive Brand Models plotted on Weibull paper.  Black step function is the truncated adjusted Kaplan-Meier points.  \label{fig:first}} 
\end{figure}

To statistically compare the GLFP Models, we estimated the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with the $i$th data point removed.  The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).  We computed the elpd for all 4 models using the R package loo \cite{loo}.  When $n$ is large, the distribution of the elpd is approximately normal and different models can be statistically compared.  We calculated the difference in expected predictive accuracy for Model 4 vs 3, Model 3 vs 2, and Model 2 vs 1, as well as the standard error of the difference (Table 1).  As the model complexity increased, the expected predictive accuracy improved.  Of all the models, Model 4 had the best predictive accuracy and was significantly better than the other 3 model specifications.
